Models of lens candidates from Space Warps CFHTLS

### 2017-02-20 parts/figures.tex

\begin{figure*}
\inclGrid{kappa_map_interpol}
\caption{Mass distribution $\kappa$ for which the results
  Figures~\ref{fig:arriv}--\ref{fig:synth} were derived.
\label{fig:kappa}}
\end{figure*}

>>>>

\begin{figure*}
\inclGrid{kappa_map_interpol}
\caption{Ensemble-average mass distribution $\kappa$ for which the
  results Figures~\ref{fig:arriv}--\ref{fig:synth} were derived.  Most
  of the mass maps have a $180^\circ$-rotation symmetry, which is
  imposed by default.  For SW02 and SW57, where the lensing mass is
  clearly asymmetric, the modeller chose to turn
  off the symmetry.
\label{fig:kappa}}
\end{figure*}

### 2017-02-20 parts/stelmass.tex
editing

We make use of the \citet{2003MNRAS.344.1000B} models to derive two
functional forms of the stellar mass with respect to SDSS-$i$ band
magnitudes. The models have solar metallicity, with a Chabrier IMF,
and assume two different age trends: a ``young'' model, with a
constant 500\,Myr age at all redshifts, and an ``old'' model where the
age is the oldest one possible at each redshift, adopting a standard
$\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$ and
$\Omega_m=0.3$. We take a geometric mean of the output from these two
models as the stellar mass of the lens. This rough estimate will be
improved in future versions by use of the available optical and NIR
magnitudes to derive more accurate constrains on the stellar
populations.

In addition, we also derive halo masses for the lenses by use of the
standard abundance matching technique, whereby a comparison of the
observed stellar mass function of galaxies with the dark matter halo
mass function from N-body simulations results in a simple relation
between the two. We emphasize that this derivation of halo mass should
be considered an ``average'' estimate, and a significant scatter can
be expected as galaxies with the same stellar mass can be found in
different environments. We refer the reader to \cite{2012MNRAS.424..104L}
for an assessment of the effect of abundance matching on the
derivation of dark matter halo properties in lensing galaxies. We
follow the prescription of \citet{2010ApJ...710..903M}, namely:

\begin{equation}
\begin{aligned}
\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
                                     (\Mhalo/M_1)^\gamma} \\
C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
\beta &= 1.057, \quad \gamma = 0.556.
\end{aligned}
\end{equation}
and define a halo-matching index:
\begin{equation}
\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
\end{equation}
that relates the observed lensing to stellar mass, with the
global ratio expected if the host halo corresponds to the
average value derived by abundance matching. Several cases
for $\haloindex$ can be considered:
\begin{itemize}
\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
  lensing mass.
\item $0 < \haloindex < 1$ is the typical situation, where the lens
  includes stars and dark matter, but not the full halo.
\item $\haloindex = 1$ means that the lens consists of the entire halo.
\item $\haloindex > 1$ is in tension with abundance-matching, because the
  lensing mass exceeds the expected halo mass.
\end{itemize}

>>>>

We make use of the \citet{2003MNRAS.344.1000B} models to derive two
functional forms of the stellar mass with respect to SDSS-$i$ band
magnitudes. The models have solar metallicity, with a Chabrier IMF,
and assume two different age trends: a ``young'' model, with a
constant 500\,Myr age at all redshifts, and an ``old'' model where the
age is the oldest one possible at each redshift, adopting a standard
$\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$ and
$\Omega_m=0.3$.

Figure~\ref{fig:stelmass} \todo{Fix overlapping labels SW28/SW29.}
shows a comparison of stellar and total masses.  The comparatitvely
large uncertainty in the stellar mass will be improved in future work
by using available optical and NIR magnitudes to derive more accurate
constrains on the stellar populations.

In addition, we also derive halo masses for the lenses by use of the
standard abundance matching technique, whereby a comparison of the
observed stellar mass function of galaxies with the dark matter halo
mass function from N-body simulations results in a simple relation
between the two. We emphasize that this derivation of halo mass should
be considered an ``average'' estimate, and a significant scatter can
be expected as galaxies with the same stellar mass can be found in
different environments. We refer the reader to \cite{2012MNRAS.424..104L}
for an assessment of the effect of abundance matching on the
derivation of dark matter halo properties in lensing galaxies. We
follow the prescription of \citet{2010ApJ...710..903M}, namely:
\begin{equation}
\begin{aligned}
\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
                                     (\Mhalo/M_1)^\gamma} \\
C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
\beta &= 1.057, \quad \gamma = 0.556.
\end{aligned}
\end{equation}
and define a halo-matching index:
\begin{equation}
\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
\end{equation}
that relates the observed lensing to stellar mass, with the
global ratio expected if the host halo corresponds to the
average value derived by abundance matching. Several cases
for $\haloindex$ can be considered:
\begin{itemize}
\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
  lensing mass.
\item $0 < \haloindex < 1$ is the typical situation, where the lens
  includes stars and dark matter, but not the full halo.
\item $\haloindex = 1$ means that the lens consists of the entire halo.
\item $\haloindex > 1$ is in tension with abundance-matching, because the
  lensing mass exceeds the expected halo mass.
\end{itemize}
This is the last of our model diagnostics, expressing whether the
lensing mass is plausible given the light from the candidate lensing
galaxy.

### 2017-02-20 parts/summary.tex
morphological diagnostics described
missded those images???

This work follows up on lens candidates reported in
\cite{2016MNRAS.455.1191M} from citizen-science volunteers, with
modelling.  Volunteers role is collaborative.  No robotic competitors.

Table~\ref{tab:models} characterises each modelled system is
(i)~according to the image morphology and how clear or indistinct it
is, (ii)~whether the mass map and synthetic lensed image appear to be
plausible, and (iii)~how the model mass compares with the estimated
stellar and full-halo masses.  Missing rows are due to photometry data
not available.

Figure~\ref{fig:stelmass} summarises the properties of the lens
candidates.  Most appear to have stellar and total mass typical of
massive ellipticals.  SW05 is the most massive of all the candidates,
with a galaxy-group scale mass.  Two systems, SW19 and SW42 have low
mass; the lens models are not entirely satisfactory, but seems
plausible.  If these are lenses, they are very interesting.  In
particular SW42 could be the most dark-matter dominated lens known.

>>>>

Table~\ref{tab:models} is a summary of our results.  It characterises
each modelled system with seven diagnostics, indicating (a)~the image
morphology and how clear or indistinct it is, (b)~whether the mass map
and synthetic lensed image appear to be plausible, and (c)~how the
model mass compares with the estimated stellar and full-halo masses.
Missing rows are due to photometry data not available.

Figure~\ref{fig:stelmass} is another summary.  It shows most of the
candidates having stellar and total mass typical of massive
ellipticals.  SW05 is the most massive of all the candidates, with a
mass of galaxy-group scale.  It is a particularly attractive system
for follow-up observations at higher resolution, as it large system
with clear multiple-image features, and modelling leaves little doubt
that it is a lens.  The two lowest-mass systems, SW19 and SW42, are
important if they are indeed lenses, because of their low mass.  The
models in both cases are plausible but not entirely satisfactory.

The trend in Figure~\ref{fig:stelmass}, that higher-mass galaxies get
progressively more dark-matter dominated, is expected and gratifying
to see.  With future data, it would be interesting to compare enclosed
stellar and total mass as a function of radius, going from
star-dominated inner regions to dark halos.
\cite{2011ApJ...740...97L} illustrate this behaviour in their
Figure~5, but the present sample could go an order of magnitude higher
in mass.
